|

### 2020-12-06 appendix/appendix.Rmd
editing the appendix and the manuscript

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.

@@

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.

@@

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.

@@

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

@@

1. Unpublished papers report significantly higher coefficients.
2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

@@

1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
2. All other coefficients remained insignificant.

@@

# Robustness: Full Model Meta-Regressions

>>>>

[^freire]: Independent Researcher, <danilofreire@brown.edu>, <http://danilofreire.github.io>. Corresponding author.

@@

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
5. Regarding statistical models, passing from `OLS` to `PANEL` increases the detected effects.

@@

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4. Regarding statistical models, passing from `OLS` to `PANEL` or `IV` increases the detected effects.

@@

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4. Regarding statistical models, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

@@

1. Unpublished papers report significantly higher coefficients.
2. Moving from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

@@

1. In terms of the modelling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
2. All other coefficients remained insignificant.

@@

# Robustness: Meta-Regressions with Our Complete Sample

### 2020-12-06 manuscript/article.Rmd
editing the appendix and the manuscript

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "compareGroups",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

@@

# Load packs
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)

@@

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. \citet{weingast1981political} provided
the general framework to analyse distributive politics. The authors argue that
the larger the number of legislative districts ($n$), the smaller the share of
tax burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity.
However, recent studies have questioned the validity of the "law of $1/n$", as
the theory is currently known. For instance, spending limits, strong executives,
and bicameralism may reduce the inefficiency of pork barrel projects
\citep{bradbury2009spatially,chen_malhotra_2007,primo2006stop}. Moreover,
\citet{primo2008distributive} affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may
hold, wherein a higher number of legislators in small constituencies decrease
the overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry \citep{doucouliagos2008democracy}.

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our sample
(`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))` papers in our review, we include `r dim(dat)[1]`
coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we add every outcome reported in the
papers, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.

Aggregate results show that council size has no significant impact on public
spending. However, the meta-regressions suggest that our study sample has high
levels of heterogeneity, and effects differ substantially according to research
design specifications. Whereas earlier studies employing convention spending
regressions often find a positive relation between legislature size and
government budgets, recent studies that use new methods of causal inference,
specially those with regression discontinuity designs, provide consistent
evidence for a negative relation. This goes in contrast with the original
theory and supports the existence of a "reverse law of $1/n$".
\textbf{Moreover, ...}  In summary, our results point out that if legislature
size affects government budgets, they do so under specific conditions and are
mediated by domestic factors.

@@

After applying our exclusion criteria, the search produced a dataset of 26
studies as of the 21\textsuperscript{st} of November, 2019. Table
\ref{tab:papers} contains the full list of articles from which we drew data. A
PRISMA\footnote{The Preferred Reporting Items for Systematic Reviews and
  Meta-Analyses (PRISMA) statement provides a checklist designed to improve the
quality and transparency of study selection processes in meta-analyses. For more
information on the PRISMA framework, see \citet{liberati2009prisma}.} flow
diagram showing the number of resulting papers after each review step is
available in the Supplementary Material.

@@

One may ask why we find no clear-cut evidence in favor or against the theory. The theory renders simple and testable empirical regularities in both of its forms, the "law of $1/n$" and the reverse "law of $1/n$." However, the empirical accessment is far from uniform in its findings. One reason may be the fact that the academic reward in social sciences for accumulating evidence is small, and most papers add features to their theory and further tests while acessing the "law of $1/n$". For instance, in our sample, papers added to the theory supermajority rules [@lee2015supermajority; @lee2016supermajority], redistricting [@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay between upper and lower houses [@chen_malhotra_2007], among others. This has the benefit of enriching the original theory with useful details, but has the disadvantage of providing less clear and decisive tests to the "law of $1/n$" theory. To solve this problem, we need more direct tests of the theory, preferably using well causally identified techniques, such as regression discontinuity design. [XXXX DANILO CHECAR]

>>>>

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

@@

# Load packages
lapply(pkgs, require, character.only = T)
devtools::install_github("isubirana/compareGroups")
library("compareGroups")

@@

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. @weingast1981political provided the
general framework to analyse distributive politics. The authors argue that the
larger the number of legislative districts ($n$), the smaller the share of tax
burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity. The
first studies that assessed the "law of $1/n$", as the theory is currently
known, mostly found a positive correlation between government spending and the
number of legislature seats, although the effect was sometimes limited to the
lower house [e.g., @baqir1999districts; @bradbury2001legislative;
@gilligan1995deviations]. However, recent studies have questioned the validity
of the theory. For instance, spending limits or strong executives may reduce
the inefficiency of pork barrel projects [@chen_malhotra_2007; @primo2006stop].
Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a "reverse law of $1/n$" may
hold, wherein a higher number of legislators in small constituencies decrease
the overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry [@doucouliagos2008democracy].

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
use quantitative methods to assess the impact of legislature size over
government spending across several dimensions. We run two sets of models: the
first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our
sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
papers in our review, we include `r dim(dat)[1]`
coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))`
articles report separate estimates
for the impact of lower and upper house size on government expenditures. In the
full model, we add every outcome reported in the papers, regardless of whether
the coefficient comes from the main tables or from robustness checks. We
discuss our sampling process in the Methods section and in the
Supplementary Material.} Our independent variables consist of three measures,
namely the size of the lower chamber ($n$), its natural logarithm (log($n$)),
and the number of members in the upper chamber ($k$). We evaluate their effect
upon public expenditure per capita, the natural logarithm of public expenditure
per capita, and government expenditure as a percentage of GDP. We then estimate
if the results vary according to four potential sources of effect
heterogeneity.

Aggregate results show that council size has no significant impact on public
spending. However, the meta-regressions suggest that our study sample has high
levels of heterogeneity, and effects differ substantially according to the
study design. We find that a reliable predictor of effect size is the research
method employed in the original paper. While earlier studies that employed
conventional linear regressions often find a positive relation between
legislature size and government budgets, recent studies that use new methods of
causal inference, specially those with regression discontinuity designs,
provide consistent evidence for a negative relation. This goes in contrast with
the original theory and supports the existence of a "reverse law of $1/n$".

@@

After applying our exclusion criteria, the search produced a dataset of `r length(unique(dat$id))` 
studies as of the 21\textsuperscript{st} of November, 2019. Table
\ref{tab:papers} contains the full list of articles from which we drew data. A
PRISMA\footnote{The Preferred Reporting Items for Systematic Reviews and
  Meta-Analyses (PRISMA) statement provides a checklist designed to improve the
quality and transparency of study selection processes in meta-analyses. For more
information on the PRISMA framework, see \citet{liberati2009prisma}.} flow
diagram showing the number of resulting papers after each review step is
available in the Supplementary Material.

@@

One may ask why we find no clear-cut evidence in favour or against the theory.
Although the literature renders simple and testable empirical regularities in both of its
forms, the "law of $1/n$" and the reverse "law of $1/n$", the
empirical assessment is far from uniform in its findings. One reason may be the
fact that the academic reward in social sciences for accumulating evidence is
small, and most papers add features to their theory and further tests while
accessing the "law of $1/n$". For instance, in our sample, papers added to the
theory supermajority rules [@lee2015supermajority; @lee2016supermajority],
redistricting [@baqir2002districting; @lee2018court], party ideology
[@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits
[@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay
between upper and lower houses [@chen_malhotra_2007], among others. This has
the benefit of enriching the original theory with useful details, but has the
disadvantage of providing less clear and decisive tests to the "law of $1/n$"
theory. To solve this problem, we need more direct tests of the theory,
preferably using well causally identified techniques, such as regression
discontinuity design. [XXXX DANILO CHECAR]
